%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Adapted by:
% Matthew Olivetti <matthewolivetti@gmail.com>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=.63in, top=.63in, right=.63in, bottom=.63in, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
% \photo[circle,edge,left]{profile}
\name{Matthew}{Olivetti}
\position{Full-Stack Web Developer{\enskip\cdotp\enskip}M.S. Cybersecurity}
\address{805 W Moorhead Cir Apt C, Boulder CO 80305}

\mobile{843-301-1744}
\email{matthewolivetti@gmail.com}
% \homepage{www.matthewolivetti.com}
\github{molivetti}
\linkedin{matthewolivetti}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \extrainfo{extra informations}

% \quote{}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Carbon Black Recruitment Team}
  {Carbon Black, Inc.\\1433 Pearl Street\\Boulder, CO 80302}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for Threat Full Stack Application Engineer}
% How the letter is opened
\letteropening{Dear Hiring Manager,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
% \letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[C]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Matthew Olivetti~~~·~~~Cover Letter}
  {}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

With five years of hands-on experience efficiently coding websites and applications focused on big data visualization using modern web technologies (HTML5, CSS3, and JavaScript), I offer the technical expertise for your full-stack web application developer position advertised on your website. 

Since earning my M.S. in Cybersecurity, I have served as a full-stack web developer at Cavulus, provider of the premier member acquisition software and technology-enabled service solutions to the health insurance industry. In this position, I have contributed to the development of front-end applications using modern web technologies by having led web development projects that generate usable and beautiful ways that present timely and voluminous amounts of sensitive healthcare data.

With a lifelong fascination with cybersecurity, I bring to the table a motivated, passionate employee who will deliver by always taking initiative. The Carbon Black suite of cybersecurity products are held to a high esteem, and the opportunity to build and extend its capabilities excites me. 

Please review my résumé, which provides details of these projects and examples of skills in:

\begin{itemize}
	\item JavaScript expertise and working knowledge of Node.js and Angular.
	\item Analytics \& data visualization experience. Numerous projects successfully delivered using D3.js, DataTables, Bootstrap, jQuery UI, HighchartsJS, etc.
	\item Responsive web development using Bootstrap, Chrome DevTools' Device Mode, Microsoft IE Virtual Machines
	\item Familiarity with modern project management tooling. Using Git on the command line npm.
	\item Full stack experience improving load time through SQL refactoring of relational databases storing highly voluminous amounts of sensitive data.
\end{itemize}

      
As a free-lance web developer focused on customer satisfaction by working closely with my clients, I manage all aspects of web development from concept to requirements definition, design, development, launch, maintenance and user support. I enjoy the client-facing role and working closely with team members to produce high-quality deliverables.
I look forward to learning more about the position. If my skills match your requirements, please contact me at (843) 301-1744 or matthewolivetti@gmail.com to schedule a meeting. Thank you.

\end{cvletter}

%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}
