%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Front End Developer} % Job title
    {Red Ventures} % Organization
    {Charlotte, NC} % Location
    {December 2019 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Owned front end development of Apple Card landing pages.}
        \item {Constructed and implemented its own SCSS framework that adhered to Apple's style guide.}
        \item {Led development stack overhaul to improve efficiency through simplicity that utilized Gulp, Bootstrap, plain Javascript, and in-house tools for compilation, compression, hosting and deployment.}
        \item {Constantly communicated between business and design teams to address and fulfill volatile requirements.}
        % \item {Improved effectiveness of Apple Card acquisition campaigns by 20-50\%.}
        \item {Developed complex solution to circumvent iOS restrictions on universal links to allow redirects and user event tracking between the browser and iOS system-level dialog boxes.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer II} % Job title
    {Scientific Research Corporation} % Organization
    {Charleston, SC} % Location
    {Jan. 2019 - July 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed core PHP platform for naval operations using LAMP stack that served thousands of active daily users.}
        % \item {Provided insight for new features and spearheaded implementation that streamlined big-data operations.}
        \item {Took initiative to modernize UI by creating a style guide using Bootstrap and FontAwesome.}
        \item {Initialized robust unit testing suites with hundreds of test cases for the platform using PHPUnit.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Freelance Software Developer} % Job title
    {Self-Employed} % Organization
    {Remote - Charleston, SC} % Location
    {Dec. 2017 - Jan. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Applied and maintained consistent, responsive Bootstrap styling and functionality for Squarespace websites.}
        \item {Developed Squarespace knowledge commerce plugin for customizing and administrating health programs with a prioritized UI/UX for its subscription members.}
        \begin{itemize}
          \vspace{1.0mm}
          \item {Frontend: jQuery, JSON-T, AJAX calls, promises, Bootstrap, HTML5, CSS3, LESS, and the YouTube API.}
          \vspace{1.0mm}
          \item {Backend: custom Squarespace elements built for content storage through the WYSIWYG editor.}
        \end{itemize}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full-Stack Developer} % Job title
    {Cavulus} % Organization
    {Hilton Head Island, SC} % Location
    {Aug. 2015 - Nov. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Part of the agile development team handling the company's flagship web app that automates and streamlines marketing, sales, enrollment, retention and compliance operations for health insurance companies.}
        %\item {Part of the agile development team handling the company's flagship web app that provides end-to-end solutions for targeting, acquiring, managing and retaining customers for health insurance companies.}
        % \begin{itemize}
        %   \vspace{1.0mm}
        %   \item {During this time, \keyword{clientele membership grew 20\%} faster than the industry average.}
        % \end{itemize}
        \item {Implemented style guide that integrated Bootstrap, D3.js, and DataTables for a cross-browser, responsive user experience with improved data visualization and performance.}
        % \item {Improved \keyword{data visualization} throughout the web application by incorporating \keyword{D3.js} and \keyword{DataTables} in the web design style guide.}
        % \item {Optimized large, complex legacy SQL queries used for the application's core operations that eliminated a total of \keyword{800 hours per day} of loading time occurred by 36,000 total active users.}
        % \item {Tuned the frontend of the web app using JavaScript, jQuery, ColdFusion, CSS3 and HTML5 to reduce \keyword{720 hours per day} of loading time experienced by 36,000 total active users.}
        % \item {Eliminated 800 hours per day of loading time experienced by 36,000 total active users by optimizing large, complex legacy SQL queries essential to the application's core operations.}
        % \item {Reduced 720 hours per day of loading time experienced by 36,000 total active users by tuning the frontend of the web app using JavaScript, jQuery, ColdFusion, CSS3 and HTML5.}
        \item {Eliminated 1520 hours/day of loading time for 36,000 total users by optimizing large, complex legacy SQL queries and updating front end using JavaScript, jQuery, ColdFusion, CSS3 and HTML5.}
        % \item {Took initiative and automated enrollment count process saving the dev team 5 man hours/week. Developed a ColdFusion app to web scrape, validate, and import data to a MySQL server and generate monthly reports.}
        % \item {Built interactive map of America's counties to visually compared their healthcare plan enrollment information. Incorporated JavaScript, jQuery, ColdFusion, Bootstrap, D3.js, AJAX, and MySQL Server.}
        % \item {Updated corporate site for responsiveness and cross-browser compatibility using Bootstrap, HTML5, and CSS3.}
        % \item {Programmed brokerage data intake process that provided cross-browser compatibility and client- \& server-side validation using JavaScript, jQuery, ColdFusion, Bootstrap, MySQL Server and a SFTP server.}
      \end{cvitems}
    }

%---------------------------------------------------------

\end{cventries}
